%%
%% This is file `./samples/longsample.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% apa7.dtx  (with options: `longsample')
%% ----------------------------------------------------------------------
%% 
%% apa7 - A LaTeX class for formatting documents in compliance with the
%% American Psychological Association's Publication Manual, 7th edition
%% 
%% Copyright (C) 2019 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% ----------------------------------------------------------------------
%% 
\documentclass[man]{apa7}

\usepackage{lipsum}

\usepackage[american]{babel}

\usepackage{indentfirst}

\usepackage{csquotes}

\usepackage[style=apa,sortcites=true,sorting=nyt,backend=biber]{biblatex}
\DeclareLanguageMapping{american}{american-apa}
\addbibresource{Week 4.bib}



\begin{document}


\setlength{\parindent}{10ex}
According to \textcite{Greco}, employees are taking more of an active role in the management of their careers. Part of this management is the setting of goals or career aspirations. Career goals are important because they can provide direction for a career trajectory and help guide the individual focus on what is important \parencite{Greco}. It's very important for me to reflect on where my life has been because I believe it will help me establish goals, both short-term and long-term, that will allow me a lead a fulfilling life.

\setlength{\parindent}{10ex}
In my opinion, I've lead an interesting life. I spent the '90s playing drums all across the Southeast. During the week I worked jobs in construction or retail and then travel and play on the weekends. I graduated with my AS in General Studies in 1996. It wasn't until 2003 that I decided to change careers and go back to school. I finished my BS in Information Technology in three semesters, worked a year, then it was off to graduate school. I received my Masters in Information Systems in 2007 then I started teaching and working as a software developer at Motlow State Community College. I left Motlow in 2011 for a civilian Army job that lasted about a year, then I went to work for a software startup until 2013. I started at Cubic in the Fall of that same year.

\setlength{\parindent}{10ex}
My short-term goals are ones that will help me finish the DSL program. One such goal is to become a better writer and communicator. I write code for a living and most of my writing is that or documenting the code. Code documenting is typically short and concise, not well-formed sentences. And when I am communicating to co-workers, I write like I talk which isn't always well-formed either. 

\setlength{\parindent}{10ex}
I believe that becoming a better writer and communicator can also be a long-term goal. I want to always be improving. I also want to learn more about the Bible. I believe that I know what it means to be a Christian in my heart but I want to know more about how to be one in my mind. I want to know know more academically, really get into the Bible and the related scholarship.

\setlength{\parindent}{10ex}
My career aspirations are a bit varied. I'd like to return to academia at some point and having a doctorate will help with that. According to a study, married doctoral graduates are more likely to pursue faculty careers than their single counterparts \parencite{Seo}. Since I'm married, I fit the description. I also have thought about being the CIO of a university with the hopes of transitioning to the president at some point. I have a special place in my heart for Motlow State, which is my local college and I would love to give back.

\setlength{\parindent}{10ex}
As an amateur triathlon, my dream job would be CEO of World Triathlon Corporation a.k.a Ironman. \textcite{Mac} found that amateur athletes that also have a career in their chosen sport are more likely to be successful in that career. The study also found that in particular, triathletes are very good at negotiation and leading \parencite{Mac}.

\setlength{\parindent}{10ex}
It doesn't matter what our short-term and long-terms goals are if we don't first glorify God in what we do. God has a grand purpose for our lives and it's important that we try to use our skills as part of that purpose \parencite{Merida2015}. I want to make sure that everything I do, I do for Him.



\printbibliography


\end{document}

%% 
%% Copyright (C) 2019 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% This work is "maintained" (as per LPPL maintenance status) by
%% Daniel A. Weiss.
%% 
%% This work consists of the file  apa7.dtx
%% and the derived files           apa7.ins,
%%                                 apa7.cls,
%%                                 apa7.pdf,
%%                                 README,
%%                                 APA7american.txt,
%%                                 APA7british.txt,
%%                                 APA7dutch.txt,
%%                                 APA7english.txt,
%%                                 APA7german.txt,
%%                                 APA7ngerman.txt,
%%                                 APA7greek.txt,
%%                                 APA7czech.txt,
%%                                 APA7turkish.txt,
%%                                 APA7endfloat.cfg,
%%                                 Figure1.pdf,
%%                                 shortsample.tex,
%%                                 longsample.tex, and
%%                                 bibliography.bib.
%% 
%%
%% End of file `./samples/longsample.tex'.
